A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-07-09 docs/methods/erosion_methods.tex
NM

To remove the effect of increasing flow rate, we show in Fig.~\ref{fig:mbodyplots}(d) the drag normalized by $\umax$. Since both the pressure and viscous drag depend linearly on $\umax$, this normalized quantity, $F_D / (4 \pi \umax)$, is {\em independent} of $\umax$ and therefore isolates how drag depends on the configuration of bodies. In this way, we can interpret $F_D / (4 \pi \umax)$ as the {\em resistance} associated with the porous network. As seen in the figure, the medium's resistance decreases rapidly as its constituents erode. Since the vertical axis is logarithmic, the rate is roughly exponential at early times. As before, the reduction in area-fraction is not sufficient to explain this rapid decline, leaving the channelization process as the most likely mechanism.

>>>>

To remove the effect of increasing flow rate, we show in Fig.~\ref{fig:mbodyplots}(d) the drag normalized by $\umax$. Since both the pressure and viscous drag depend linearly on $\umax$, this normalized quantity, $F_D / (4 \pi \mu \umax)$, is {\em independent} of $\umax$ and therefore isolates how drag depends on the configuration of bodies. In this way, we can interpret $F_D / (4 \pi \mu \umax)$ as the {\em resistance} associated with the porous network. As seen in the figure, the medium's resistance decreases rapidly as its constituents erode. Since the vertical axis is logarithmic, the rate is roughly exponential at early times. As before, the reduction in area-fraction is not sufficient to explain this rapid decline, leaving the channelization process as the most likely mechanism.

### 2018-07-09 docs/methods/revisions.tex
NM

\noindent
\comment{On page 23: the scaling of Fd with 4*pi*U is not dimensionless.
It seems to me like the drag coefficient might be a better quantity to
base the discussion on.}
\begin{itemize}
  \item 
\end{itemize}

>>>>

\noindent
\comment{On page 23: the scaling of Fd with 4*pi*U is not dimensionless.
It seems to me like the drag coefficient might be a better quantity to
base the discussion on.}
\begin{itemize}
\item Yes, we agree that it makes more sense to make this normalization dimensionless.  Accordingly, we have now included the viscosity in the denominator, so that we are dealing with the quantity $F_D /(4 \pi \mu U)$. This modification does not actually change the numbers in the plot since we have already set $\mu =1$ to non-dimensionalize, but it would make it easier to apply our results to laboratory or field studies (which is a driving interest of ours).

As a side-note, in case you are concerned that there should be a lengthscale included in the denominator, remember that, since these are 2D simulations, $F_D$ is actually the drag-per-unit span (as discussed in Section 5.2).
\end{itemize}
